Supplement to 'Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-09-01 doc/supplemental.Rmd
added figure to supplemental

```{r packages, include=FALSE}
library(tidyverse)
library(patchwork)
library(flextable)
library(tsibble)
library(lubridate)
library(latex2exp)
library(colorspace)
library(glue)
library(performance)
source(here::here("R", "utils.R"))
```

@@

```{r}
withr::with_dir(here::here(), {
  targets::tar_load(c(
    s_cf,
    s_1ha,
    g_cf,
    g_1ha,
    f_cf,
    f_1ha,
  ))
})
```

@@

```{r}
library(ggpointdensity)
size_curves <- 
  map_df(list(CF = g_cf, "1-ha" = g_1ha), ~{
    smooth_estimates(.x, smooth = "s(log_size_prev)", unconditional = TRUE, overal_uncertainty = TRUE) %>% add_confint() %>% 
      add_column(intercept = coef(.x)[1]) %>% 
      mutate(across(c(est, lower_ci, upper_ci), ~.x + intercept))
  },
  .id = "habitat")

@@

@@

```{r fig.width=7, fig.height=7}
library(patchwork)
(g + theme(axis.title.x = element_blank()))/
(s + theme(axis.title.x = element_blank()))/
(f) + plot_annotation(tag_levels = "a")
```

>>>>

```{r packages, include=FALSE}
library(tidyverse)
library(patchwork)
library(flextable)
library(tsibble)
library(lubridate)
library(latex2exp)
library(colorspace)
library(glue)
library(performance)
library(gratia)
library(ggpointdensity)
source(here::here("R", "utils.R"))
```

@@

```{r}
withr::with_dir(here::here(), {
  tar_load(c(
    s_cf,
    s_1ha,
    g_cf,
    g_1ha,
    f_cf,
    f_1ha
  ))
})
```

@@

```{r}
size_curves <-
  map_df(list(CF = g_cf, "1-ha" = g_1ha), ~{
    smooth_estimates(.x, smooth = "s(log_size_prev)", unconditional = TRUE, overal_uncertainty = TRUE) %>% add_confint() %>%
      add_column(intercept = coef(.x)[1]) %>%
      mutate(across(c(est, lower_ci, upper_ci), ~.x + intercept))
  },
  .id = "habitat")

@@

```{r fig.width=7, fig.height=7}
(g + theme(axis.title.x = element_blank()))/
(s + theme(axis.title.x = element_blank()))/
(f) + plot_annotation(tag_levels = "a")
```

@@
